Coherent optical association of a single molecule

### 2020-10-08 paper.tex
Update on Overleaf.

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2. KW: The 2 in the denominator is including cross coupling. 4 without cross coupling. Since cross coupling is mentioned later, maybe leave this with 4?}, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state. The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. \textcolor{blue}{(blue text can potentially be moved to footnote) Furthermore, because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power. %There is
  An additional factor of 2 is included in the scattering rate because the molecular state scatters off of both Raman beams at roughly the same single photon detuning. } Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred while achieving a realistic Raman Rabi frequency. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states. %There are also many possible intermediate states to choose from.

@@

\textcolor{blue}{Main point here. Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree. I want to layout the structure .... motivate for the better ratio first, than talk about choosing the state.} \textcolor{red}{KW: Okay, got it. Makes sense. }
In addition to the intermediate state, the choice of the initial and final states is also critical. As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. This ratio can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states. Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. \textcolor{red}{KW: Can also include similar footnote here about cross coupling? The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination. (We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

>>>>

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate is $ \Omega_a\Omega_m / 2\Delta$ accompanied by a photon scattering rate of $\Gamma_e \Omega^2 / 4\Delta^2$...(sum of i terms\textcolor{red}{KW: I was intending to only mention the sum over terms at the end when we exit the 3 level system.})\textcolor{blue}{check factor of 2. KW: The 2 in the denominator is including cross coupling. 4 without cross coupling. Since cross coupling is mentioned later, maybe leave this with 4?}, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state. The scattering rate therefore predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. \textcolor{blue}{(blue text can potentially be moved to footnote) Furthermore, because the energy difference of the atomic and the weakly bound states are small ($<$1~GHz) comparing to $\Delta$, the power of the Raman beams are chosen to be equal to gives the largest Raman Rabi rate at a fixed total power. %There is
  An additional factor of 2 is included in the scattering rate because the molecular state scatters off of both Raman beams at roughly the same single photon detuning. } Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred while achieving a realistic Raman Rabi frequency. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rates and Rabi rates become a sum of the scattering rates and Rabi rates over all the states. %There are also many possible intermediate states to choose from.

@@

%\textcolor{blue}{Main point here. Small $\Omega_a/\Omega_m$ ratio can be compensated by larger detuning, but Stark shift is problematic.} \textcolor{red}{KW: I agree Stark shift limitation is definitely pretty problematic, but I would also argue that larger detuning may not be able to save the day, because of the many vibrational states in a molecular potential, the lower Raman rabi frequency which results from detuning farther and possibly running into other limitations if you have to do that, such as the background off resonant scattering rate from near threshold states or technical background scattering.} \textcolor{blue}{yes, I agree. I want to layout the structure .... motivate for the better ratio first, than talk about choosing the state.} \textcolor{red}{KW: Okay, got it. Makes sense. }
%In addition to the intermediate state, the choice of the initial and final states is also critical. 
As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $. \textcolor{red}{KW: Can also include similar footnote here about cross coupling? The 2 in the denominator is assuming cross coupling and equal powers.} The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states. In particular, it can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, among the stable spin combinations, 4422 and 3311 both have small scattering lengths of $ a_{4422}= 30.4a_0, a_{3311} = 13.7a_0 $ respectively, but the 3332 combination has a large and negative scattering length of $ a_{3322} = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the 3322 hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in the 3322 spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the 4422 and 3311 bound states. Therefore, using an initial 3322 hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the 4422 or 3311 combinations. 
%Thus, instead of a required intensity stability of $0.3 \% $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5\% $.  
Thus, we choose the 3322 spin combination as our initial state and drive to the first bound state for the 3322 spin combination. (We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)
